Writing a reproducible paper with RStudio and Quarto

### 2023-03-20 paper.qmd
Small edits.

``` {{r}}
#| label: tbl-4
#| tbl-cap: "Summary: Numeric variables"
library(modelsummary)
datasummary_skim(swiss, 
                 type="numeric", 
                 histogram=T,
                 output="flextable", # adjust to html for HTML output
                 title = "Summary: Numeric variables")
```

@@

if(knitr::is_latex_output()){outputformat <- "flextable"}
if(knitr::is_html_output()){outputformat <- "html"}

library(modelsummary)
datasummary_skim(swiss, 
                 type="numeric", 
                 histogram=T, 
                 output= outputformat,
                 title = "Summary: Numeric variables")
```

@@

library(flextable)
tab_cat <- datasummary_skim(swiss, 
                            type="categorical", 
                            output = 'flextable')  # adjust to html for HTML output

@@

@@

library(gt)
library(gtsummary)
# additionally we want to change the font, font size and spacing
modelsummary(models,
             output = 'gt',
             notes = "Notes: some notes...") %>%
    tab_spanner(label = 'Dependent variable: Fertility', columns = 2:4) %>%
  tab_options(
    table.font.size = 10,
    data_row.padding = px(1),
    table.border.top.color = "white",
    heading.border.bottom.color = "black",
    row_group.border.top.color = "black",
    row_group.border.bottom.color = "white",
    table.border.bottom.color = "white",
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
  )
```

@@

if(knitr::is_html_output()){table7}else{table7 %>% gt::as_latex() %>% as.character() %>% gsub("\\(Intercept\\)", "Intercept", .) %>% cat()}

```

>>>>

``` {{r}}
#| label: tbl-4
#| tbl-cap: "Summary: Numeric variables"
library(modelsummary)
datasummary_skim(swiss, 
                 type="numeric", 
                 histogram=T,
                 output="flextable",
                 title = "Summary: Numeric variables")
```

@@

library(modelsummary)
datasummary_skim(swiss, 
                 type="numeric", 
                 histogram=T, 
                 output= "flextable",
                 title = "Summary: Numeric variables")
```

@@

@@

library(dplyr)
tab_cat <- tab_cat %>%
  font(fontname="Times New Roman", part="header") %>%
  font(fontname="Times New Roman", j=1:4) %>%
  fontsize(size=12, part="header") %>%
  fontsize(size=12, j=1:4) %>%
  line_spacing(space = 0.3, part = "all")

@@

library(gt)
library(gtsummary)
# additionally we want to change the font, font size and spacing
modelsummary(models,
             output = 'gt',
             notes = "Notes: some notes...") %>%
    tab_spanner(label = 'Dependent variable: Fertility', columns = 2:4) %>%
  tab_options(
    table.font.size = 10,
    data_row.padding = px(1),
    table.border.top.color = "white",
    heading.border.bottom.color = "black",
    row_group.border.top.color = "black",
    row_group.border.bottom.color = "white",
    table.border.bottom.color = "white",
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
  )

# Produce right output depending on format (html vs. latex)
if(knitr::is_html_output()){table7}else{table7 %>% gt::as_latex() %>% as.character() %>% gsub("\\(Intercept\\)", "Intercept", .) %>% cat()}
```

@@

if(knitr::is_html_output()){table7}else{table7 %>% gt::as_latex() %>% as.character() %>% gsub("\\(Intercept\\)", "Intercept", .) %>% cat()}
```
